Microlensing as a possible probe of the internal structure of quasars

### 2015-05-12 paper1/fitting.tex
two columns?
editing

\begin{figure}
\centering
\includegraphics[width=0.48\hsize]{plots/data_cc.eps}
\includegraphics[width=0.48\hsize]{plots/data_dd.eps}
\includegraphics[width=0.48\hsize]{plots/data_gg.eps}
\includegraphics[width=0.48\hsize]{plots/burnin_cg.eps}
\caption{\label{fig:datafitting} Three different mock datasets (in black) -- crescent, uniform-disk and Gaussian disk (in reading order). In each panel showing the best fit for each of the three models - crescent (red), uniform-disk (blue) and Gaussian disk (green). Bottom-right panel shows the $\chi^2$ of each step of the full MCMC for CG case (Gaussian disk data fitted with crescent source model)}. 
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.48\hsize]{plots/Rp4all.eps}
  \includegraphics[width=0.48\hsize]{plots/Rhalf4all.eps}\\
  \includegraphics[width=0.48\hsize]{plots/Rhalf_RnRp.eps}
  \includegraphics[width=0.48\hsize]{plots/aRp_bRp.eps}
\caption{\label{fig:mcmc} Top panels showing the 1D probability density function for size of the source, $R_p$ (left), and half light radius of the source, $R_{1/2}$ (right). Same color represeents the same dataset whereas same line style corresspond to same model fit. In the legend showing the reduced $\chi^2$ of the best fit in each case. Bottom two panels showing the 2$\sigma$ contours (or error ellipses) of the crescent model when fitting with the three different datasets.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{plots/data_cc.eps}
\includegraphics[width=0.9\hsize]{plots/data_dd.eps}
\includegraphics[width=0.9\hsize]{plots/data_gg.eps}
\caption{\label{fig:datafitting} Three different mock datasets with
  three different parameterisations fitted to each --- crescent (red),
  uniform-disk (blue) and Gaussian disk (green).}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{plots/burnin_cg.eps}
\caption{\label{fig:datafitting} The $\chi^2$ of each step of the full
  MCMC for one case.}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{plots/Rhalf_RnRp.eps}
  \includegraphics[width=0.9\hsize]{plots/aRp_bRp.eps}
\caption{\label{fig:mcmc} Top panels showing the 1D probability density function for size of the source, $R_p$ (left), and half light radius of the source, $R_{1/2}$ (right). Same color represeents the same dataset whereas same line style corresspond to same model fit. In the legend showing the reduced $\chi^2$ of the best fit in each case. Bottom two panels showing the 2$\sigma$ contours (or error ellipses) of the crescent model when fitting with the three different datasets.}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize]{plots/Rp4all.eps}
\caption{\label{fig:mcmc} Posterior probability distribution for size
  of the source, $R_p$. Same color represeents the same dataset
  whereas same line style corresponds to same model fit. In the legend
  showing the reduced $\chi^2$ of the best fit in each case.}
\end{figure}
